Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-01-02 paper/paper.tex
20200102 22:22:00

\subsection{Moment direction of the FM phases}
For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., \textit{x}, \textit{y}, \textit{z} direction). However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. To extract the moment direction of the \emph{FM-A} and \emph{FM-C} phases, we construct the following cluster spin-coherent state
\begin{equation}
    |\Psi(\theta, \phi) \rangle = \bigotimes_{i=1}^N|\theta,\phi \rangle
\end{equation}
and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$. The resulting probability maps are shown in Fig. \ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).

\textcolor{red}{Moment direction of the FM phases. To be accomplished $\cdots \cdots$}

\subsection{Moment direction of the stripe phases}
\textcolor{red}{Moment direction of the stripe phases. To be accomplished $\cdots \cdots$}

>>>>

\subsection{Moment direction of the FM phases}
For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., \textit{x}, \textit{y}, \textit{z} direction). However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. To extract the moment direction of the \emph{FM-A} and \emph{FM-C} phases, we construct the following cluster spin-coherent state
\begin{equation}
    |\Psi(\theta, \phi) \rangle = \bigotimes_{i=1}^N|\theta,\phi \rangle
\end{equation}
and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$. The resulting probability maps are shown in Fig. \ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b). For the \emph{FM-A} phase, the probability map reveals the moment being constrained to the lattice plane with all directions degenerate, as expected from classical considerations (see the green dashed line). As for the \emph{FM-C} phase, the probability is clearly peaked at the direction perpendicular to the lattice plane which is also consistent with our classical analysis (marked by the green solid circle).

\subsection{Moment direction of the stripe phases}
The stripe phases have three degenerate patterns as shown in Fig. \ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern. For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig. \ref{fig:PhaseDiagram}(b) and present the probability maps in Fig. \ref{fig:Proabilities}(c)-(f) for \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D} respectively. In the HK limit, the \emph{Stripe-A} phase is connected to the \emph{FM-B} phase through FST and the spins are supposed to along the \emph{x}-axis for stripe pattern in Fig. \ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit (see Fig. \ref{fig:Proabilities}(c)). As for the \emph{Stripe-D} phase near the AF Kitaev point, the probability map Fig. \ref{fig:Proabilities}(f) reveals the moment being constrained to the vicinity of the \emph{yz} plane, as predicted by classical analysis. Within this plane, the order-from-disorder mechanism selects the cubic axes \emph{y} and \emph{z} where the probability reaches its maxima. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of six possible classical stripe states, more importantly it a signature of large quantum flucations in the ground state.

The main effect of $\Gamma$ term on \emph{Stripe-A} and \emph{Stripe-D} is tilting the moment orientation away from the cubic axes directions, yielding \emph{Stripe-B} and \emph{Stripe-C}. Fig. \ref{fig:Proabilities}(e) is a representative probability map for \emph{Stripe-B}. The probability takes maximum value at the directions determined by Eq.\eqref{eq:S1}.
\textcolor{red}{$\cdots \cdots$}
